---
title: "Bilingual Assholes Study 2: Expl Analysis"
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) 
library(stringr)
library(textstem)
library(tidyverse)
library(broom.mixed)  # for tidy()
library(ggeffects)
library(lattice)

theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../helpers.R")

d <- read.csv("../data/data_exclusions.csv")
prof <- read.csv("../data/df_italian_high_read.csv")

d_high_prof <- inner_join(d,prof, by = "Participant")

nrow(d_high_prof)
nrow(d)
nrow(prof)

length(unique(d_high_prof$Participant))
length(unique(d$Participant))
length(unique(prof$Participant))
```

```{r}
d <- d %>%
  mutate(
    LexicalType.n = ifelse(LexicalType == "adj", 0, 1),
    Nativeness.n = ifelse(Nativeness == "L1", 0, 1),
    Valence.n = ifelse(Valence == "neg", 0, 1),
    Name = as.factor(Name),
    Participant = as.factor(Participant),
    LexicalType = as.factor(LexicalType),
    ContextCondition = as.factor(ContextCondition),
    SliderResponse = as.numeric(SliderResponse),
    cNativeness = Nativeness.n-mean(Nativeness.n),
    cLexicalType = LexicalType.n-mean(LexicalType.n))
```


# Theoretical Questions


```{r}
m.s <- lmer(SliderResponse ~ ContextCondition + (1+ContextCondition|Name) + (1+ContextCondition|Participant), data = d)
summary(m.s)
```


```{r}
m.s.2 <- lmer(SliderResponse ~ ContextCondition*LexicalType + (1+ContextCondition|Name) + (1+ContextCondition|Participant), data = d)
summary(m.s.2)
```


```{r}
m.s.3 <- lmer(SliderResponse ~ ContextCondition*LexicalType*Valence + (1+ContextCondition|Name) + (1+ContextCondition|Participant), data = d)
summary(m.s.3)
```

# Does Nativeness improve model fit?

Does Nativeness influence sensitivity to contextual information or valence?
```{r}
m.n <- lmer(SliderResponse ~ ContextCondition*Nativeness + (1+ContextCondition|Name) + (1+ContextCondition|Participant), data = d)
summary(m.n)
```

```{r}
anova(m.s,m.n)
```



```{r}
m.n.2 <- lmer(SliderResponse ~ LexicalType*ContextCondition*Nativeness + (1+ContextCondition|Name) + (1+ContextCondition+LexicalType|Participant), data = d)
summary(m.n.2)
```


```{r}
m.n.3 <- lmer(SliderResponse ~ LexicalType*ContextCondition*Valence*Nativeness + (1+ContextCondition|Name) + (1+ContextCondition+LexicalType+Valence|Participant), data = d)
summary(m.n.3)
```


```{r}
anova(m.n.2,m.n.3)
```





# Valence?


```{r}

dcen <- d %>% 
  filter(Valence %in% c("pos","neg")) %>% 
  mutate(Name = as.factor(Name),
         Participant = as.factor(Participant),
         ContextCondition = as.factor(ContextCondition),
         Response = as.numeric(SliderResponse),
         cValence = Valence.n-mean(Valence.n),
         cLexicalType = LexicalType.n-mean(LexicalType.n))

m.s <- lmer(Response ~ cLexicalType*ContextCondition + (1|Name) + (1+cLexicalType+ContextCondition|Participant), data = dcen)
summary(m.s)

m.c <- lmer(Response ~ Valence*cLexicalType*ContextCondition + (1|Name) + (1+Valence+cLexicalType+ContextCondition|Participant), data = dcen)
summary(m.c)

anova(m.s,m.c)



```



# Does Nativeness explain more variance?
- No
```{r}
m.c.l <- lmer(Response ~ Nativeness*cValence*cLexicalType*ContextCondition + (1|Name) + (1+cValence+cLexicalType+ContextCondition|Participant), data = dcen)
summary(m.c.l)

anova(m.c, m.c.l)
```

# Valence and Nativeness?
```{r}
m.v.l <- lmer(Response ~ Nativeness*cValence + (1|Name) + (1+cValence|Participant), data = dcen)
summary(m.v.l)
```


## But in the TO condition
```{r}
to <- d %>% 
  filter(ContextCondition == "TO") %>% 
  filter(Valence %in% c("pos","neg")) %>% 
  mutate(Name = as.factor(Name),
         Participant = as.factor(Participant),
         ContextCondition = as.factor(ContextCondition),
         Response = as.numeric(SliderResponse),
         cValence = Valence.n-mean(Valence.n),
         cLexicalType = LexicalType.n-mean(LexicalType.n))

m.to <- lmer(Response ~ Nativeness*Valence*cLexicalType + (1|Name) + (1+cValence+cLexicalType|Participant), data = to)

summary(m.to)

```



#Negative only

```{r}

levels(d$LexicalType)
d <- d %>%
  mutate(
    LexicalType.n = ifelse(LexicalType == "adj", 0, 1)
  )

dcen <- d %>% 
  filter((TrialType == "test") & (Valence == "neg")) %>% 
  mutate(Name = as.factor(Name),
         Participant = as.factor(Participant),
         LexicalType = as.factor(LexicalType),
         ContextCondition = as.factor(ContextCondition),
         SliderResponse = as.numeric(SliderResponse),
         cNativeness = Nativeness.n-mean(Nativeness.n),
         cLexicalType = LexicalType.n-mean(LexicalType.n))


m4 <- lmer(SliderResponse ~ cLexicalType*ContextCondition + (1+ContextCondition|Name) + (1+ContextCondition+cLexicalType|Participant), data = dcen)

summary(m4)

```

# Positive

```{r}

levels(d$LexicalType)
d <- d %>%
  mutate(
    LexicalType.n = ifelse(LexicalType == "adj", 0, 1)
  )

dcen <- d %>% 
  filter((TrialType == "test") & (Valence == "pos")) %>% 
  mutate(Name = as.factor(Name),
         Participant = as.factor(Participant),
         LexicalType = as.factor(LexicalType),
         ContextCondition = as.factor(ContextCondition),
         SliderResponse = as.numeric(SliderResponse),
         cNativeness = Nativeness.n-mean(Nativeness.n),
         cLexicalType = LexicalType.n-mean(LexicalType.n))


m5 <- lmer(SliderResponse ~ cLexicalType*ContextCondition + (1+ContextCondition|Name) + (1+ContextCondition+cLexicalType|Participant), data = dcen)

summary(m5)

```



# Looking at Italian Reading Proficiency
```{r}
names(d_high_prof)

d_high_prof["ReadingProficiency"] = d_high_prof["LQ_pcibex_log_ita_proficiency_reading"]

names(d_high_prof)
d_high_prof <- d_high_prof %>% 
  # looking only at the L2 data
  filter(Nativeness == "L2") %>%
  mutate(Name = as.factor(Name),
         Participant = as.factor(Participant),
         ReadingProficiency = as.numeric(ReadingProficiency),
         ContextCondition = as.factor(ContextCondition),
         SliderResponse = as.numeric(SliderResponse),
         LexicalType = as.factor(LexicalType))
```

## Does RP determine responses?

```{r}
m <- lmer(SliderResponse ~ ReadingProficiency + (1|Name) + (1|Participant), data = d_high_prof)
summary(m)
```


```{r}
m.c <- lmer(SliderResponse ~ ContextCondition + (1|Name) + (1|Participant), data = d_high_prof)
summary(m.c)
```


## Valence and Context in HP L2
```{r}
m.c.v <- lmer(SliderResponse ~ Valence*ContextCondition + (1|Name) + (1|Participant), data = d_high_prof)
summary(m.c.v)
```

## Does valence improve fit?
```{r}
anova(m.c,m.c.v)
```

## Sensitivity to lexical items?
```{r}
m.c.v.l <- lmer(SliderResponse ~ Valence*ContextCondition*LexicalType + (1|Name) + (1|Participant), data = d_high_prof)
summary(m.c.v.l)
```

```{r}
anova(m.c.v,m.c.v.l)
```

## Including RP improves fit?
```{r}
m.c.v.l.r <- lmer(SliderResponse ~ Valence*ContextCondition*LexicalType*ReadingProficiency + (1|Name) + (1|Participant), data = d_high_prof)
summary(m.c.v.l)
```


```{r}
# anova(m.c.v.l,m.c.v.l.r)
```

