---
title: "Bilingual Assholes Study 2: LeapQ"
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(sciplot)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00")
vaPalette <- c("#FCC6BB", "#F54927", "#9C2007", "#440E03")
gPal <- c("#B9E615","#5E15E6","#F78D02", "#009E73")

# scale_fill_manual(values = vaPalette)
# valPal <- c("#F4320B")

this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../helpers.R")

d <- read.csv("../data/processed_lq.csv")
```

# Exclude participants who don't speak Italian
Due to prolific error, there were participants allowed in who were not bilingual in Italian

Participants who do not have 'italian' or substrings of it in the columns
[2] "LQ_dominance_1"                             
  [3] "LQ_dominance_2"                             
  [4] "LQ_dominance_3"                             
  [5] "LQ_dominance_4"                             
  [6] "LQ_dominance_5"                             
  [7] "LQ_acquisition_1"                           
  [8] "LQ_acquisition_2"                           
  [9] "LQ_acquisition_3"                           
 [10] "LQ_acquisition_4"                           
 [11] "LQ_acquisition_5"  


## Italian only
```{r}
cols <- c(
  "LQ_dominance_1",
  "LQ_dominance_2",
  "LQ_dominance_3",
  "LQ_dominance_4",
  "LQ_dominance_5",
  "LQ_acquisition_1",
  "LQ_acquisition_2",
  "LQ_acquisition_3",
  "LQ_acquisition_4",
  "LQ_acquisition_5"
)

df_italian <- d %>%
  filter(
    if_any(
      all_of(cols),
      ~ str_detect(str_to_lower(as.character(.)), "italian")
    )
  )

nrow(df_italian)
```

```{r}

```


## Non-italian speakers, to be excluded
```{r}
df_non_italian <- d %>%
  filter(
    if_all(
      all_of(cols),
      ~ !str_detect(str_to_lower(as.character(.)), "italian")
    )
  )

nrow(df_non_italian)
```

### Save to list the participants who must be excluded
```{r}
participant_list <- df_non_italian$Participant
length(participant_list)
write.csv(
data.frame(Participant = participant_list),
"../data/non_italian_participants.csv",
row.names = FALSE
)
```

# Graph proficiency histogram

## Reading Proficiency
```{r}
df_italian$LQ_pcibex_log_ita_proficiency_reading <- as.numeric(df_italian$LQ_pcibex_log_ita_proficiency_reading)


barplot(
  table(df_italian$LQ_pcibex_log_ita_proficiency_reading),
  xlab = "Reading proficiency",
  ylab = "Count",
  main = "Italian Reading Proficiency"
)


# remove people with proviciency including all values below 4
low_reading_poficiency <- df_italian %>% 
  filter(LQ_pcibex_log_ita_proficiency_reading < 5)

length(unique(low_reading_poficiency$Participant))
length(unique(low_reading_poficiency$Participant))/length(unique(df_italian$Participant))*100
length(unique(df_italian$Participant)) - length(unique(low_reading_poficiency$Participant))

# Save to df to exclude from graphs
write.csv(
data.frame(Participant = low_reading_poficiency$Participant),
"../data/low_reading_proficiency_participants.csv",
row.names = FALSE
)
```

```{r}
# save the reading proficiency values to .csv

df_italian_high_read <- df_italian %>% 
  filter(!Participant %in% low_reading_poficiency$Participant) %>% 
  select(Participant, LQ_pcibex_log_ita_proficiency_reading)

write.csv(df_italian_high_read,"../data/df_italian_high_read.csv")

```


## Speaking Proficiency
```{r}
df_italian$LQ_pcibex_log_ita_proficiency_speaking <- as.numeric(df_italian$LQ_pcibex_log_ita_proficiency_speaking)


barplot(
  table(df_italian$LQ_pcibex_log_ita_proficiency_speaking),
  xlab = "Speaking proficiency",
  ylab = "Count",
  main = "Italian Speaking Proficiency"
)
```

## Understanding Proficiency
```{r}
df_italian$LQ_pcibex_log_ita_proficiency_understanding <- as.numeric(df_italian$LQ_pcibex_log_ita_proficiency_understanding)


barplot(
  table(df_italian$LQ_pcibex_log_ita_proficiency_understanding),
  xlab = "Understanding proficiency",
  ylab = "Count",
  main = "Italian Understanding Proficiency"
)
```

